---
---

## Reading rasters into R

While vector spatial layers are composed of geometrical objects defined by their vertices, raster layers are grids of pixels with attached values. 

We start by loading the **raster** package in R and importing a raster file with the eponymous `raster` function. This file is a portion of the [National Land Cover Database](http://www.mrlc.gov/nlcd2011.php), which we already cropped and reduced to a lower resolution in order to speed up processing time for this tutorial.

```{r load_raster, title = "lesson-7-1.R"}
library(raster)
nlcd <- raster("data/nlcd_agg.grd")
```

<!--split-->

A raster is fundamentally a data matrix with associated spatial properties (e.g. extent, resolution and projection) that allow its values to be mapped onto geographical space. You can view these key properties -- the raster's metadata -- by typing the object name in the console.

```{r summary_raster}
nlcd
```

<!--split-->

The values in raster cells range from 0 to 255, yet land cover is a categorical variable. The mapping of numbers to categories can be found in the raster's attribute table:
```{r attr_table, title = "lesson-7-1.R"}
attr_table <- nlcd@data@attributes[[1]]
```

Each land cover category has a distinct color specified by the "Red", "Green" and "Blue" columns. 

<!--split-->

We can visualize the whole raster with `plot`.
```{r raster_plot, title = "lesson-7-1.R", fig.keep="last"}
plot(nlcd)
```

<!--split-->

At this point, we might want to superpose the county boundaries on top of the raster image. However, the following instruction does not show the county polygons. Why not?
```{r add_counties_unproj, eval = FALSE}
plot(counties_md, add = TRUE)
```
