---
---

## Reading shapefiles into R 

Vector data in shapefiles can be read via the `readOGR` function in `rgdal`,
which is a package linking R to the open source Geospatial Data Abstraction 
Library (GDAL).

Here, we read a shapefile corresponding to county boundaries for the state 
of Maryland. This data was extracted from the full county boundaries
shapefile available on the [US census website](https://www.census.gov/geo/maps-data/data/cbf/cbf_counties.html).

```{r load_shp, results = "hide", title = "lesson-7-1.R"}
library(rgdal)
counties_md <- readOGR("data/cb_500k_maryland", "cb_500k_maryland")
```

Note that the first argument to `readOGR` is the path of the shapefile 
whereas the second argument is the layer name; for simple shapefiles, it is
usually identical to the file name.

<!--split-->

The shapefile is read as a *SpatialPolygonsDataFrame* object, which contains
both a list of 24 county (multi)polygons (`counties_md@polygons`), as well as a
data frame (`counties_md@data`) where each row stores the attributes of the
corresponding county.

```{r shp_summary}
summary(counties_md)
```
